\large{\bf Looking forwards and backwards through locally regulated populations }

### 2023-01-13 forwards-and-backwards.tex
.
Update on Overleaf.

    The process we consider is similar to the state-dependent branching processes
    of \citet{KR}, so one might expect that the proofs there would carry over with little change.
    However, there is an important difference:
    Recall that the level $U_a(t)$ of a line of descent evolves as
    $$
    \dot u 
    =
    c(x, \eta)
    u^2
    - b(x, \eta) ,
    $$
    where
    \begin{align*}
        c(x, \eta) &= \frac{\theta}{N} \gamma(x, \eta) \int_{\IR^d} r(y, \eta) q(x, dy) \\
        \text{and}\qquad
        b(x, \eta)
        &=
        \theta \gamma(x, \eta) \int_{\IR^d} \left(r(y, \eta) - r(x, \eta)\right) q(x, dy)
        + F(x, \eta) 
    \end{align*}
    (see equations \eqref{eqn:level_generator} and \eqref{eqn:b_limit}),
    where $c(x, \eta) \ge 0$ and $b(x, \eta)$ may take either sign.
    In \citet{kurtz/rodrigues:2011}, $b$ was bounded above and $c$ was bounded away from zero,
    so they noted that if $U_a(t) \ge b/c$
    lines of descent would only move upwards from that time onwards.
    This allows the processes to be jointly and simultaneously constructed
    for all values of $N$, with a pointwise embedding
    of $(\xi^N_t)_{t \ge 0}$ within $(\xi^{M})_{t \ge 0}$ for $b/c < N < M$.
    In other words, individuals with levels above $N > b/c$ at time $t_0$
    do not affect $(\lp^N_t)_{t \ge t_0}$,
    thus allowing a comparison of the number of lines of descent below level $u_0$
    to a branching process.
    Although we have provided a
    joint construction of $\lp^N$ for all $N$ in Section~\ref{sec: individual lines of descent},
    it does not have this monotonicity:
    for one thing, $b$ and $c$ depend on the population process $\eta$
    and so all individuals can affect all other ones (even those with lower levels).
    Furthermore, in the deterministic case $\theta/N$ and hence $c$ converge to zero,
    and so lines of descent with arbitrarily high level may drift back downwards.
    Indeed, this must be the case if the population persists,
    since in the deterministic case there is no branching.
    In our case $b$ and $c$ depend on the state of the population,
    so we have no such monotonicity.

@@

\begin{lemma} \label{lem:tightness of levels} For fixed $a\in \mathcal{U}$, let $U^N_{a}(\tau_a)=U_0$, i.e. the level of the line of descent $a$ at birth is $U_0>0$.
On top of the assumptions laid out in Lemma \ref{lem: tightness of individual spatial trajectory}, assume that 
$$
    \sup_{\theta}\mathbb{E}\left[ \sup_{x, \eta}b_\theta(x, \eta) \right]
    :=
    \sup_{\theta}
    \theta 
    \mathbb{E}\left[ \sup_{x, \eta} \left(
    \gamma_\theta(x,\eta) \int_{\IR^d} r_\theta(y, \eta) q_\theta(x, dy)
    -
    \mu_\theta(x,\eta)
    \right)\right] 
    \leq C_G,
$$
and there exists some $C_F \geq 0$ such that
\begin{align} 
\begin{split}
b_{\theta}(x, \eta)
&=
    \theta \gamma_{\theta}(x, \eta) \int_{\IR^d} \left( r_{\theta}(y, \eta) - r_{\theta}(x, \eta) \right) q_{\theta}(x, dy)
    + F_{\theta}(x, \eta) \\
& \geq - C_F \varrho_F*\eta(x)
\end{split}
\end{align}
for all $x \in \IR^d$ and  $\eta \in \mathcal{M}_{F}(\IR^d)$.

@@

\subsection{Tightness of the Lookdown Representation}

\comment{
    This comes later because it uses convergence of the population process itself.
}

We have now proved tightness of the spatial and level process for a line of descent. To prove that the lookdown representation is tight, we generalise the vague topology to the setting of measure-valued processes. For a detailed description of the vague topology, refer to Appendix \ref{sec: Empirical Measure Topology}.

Then, we apply Theorem A.24 in \cite{kallenberg1997foundations}
(Theorem \ref{teo: Vague Relative Compactness through Projection})
and use a corollary of Stone-Weierstrass Theorem
(Lemma \ref{lem: Dense set for test functions on empirical measures})
to show that our lookdown representation $\{\xi^N_t: N \in \mathbb{N}\}$ is tight
as a $\mathcal{M}(\mathbb{R^d} \times [0, \infty])$-valued stochastic process
in the vague topology
as long as $\{F_g(\xi^N_t): N \in \mathbb{N}\}$ is tight
as real-valued stochastic processes for a huge class of $F_g$. 
Explicitly, $F_g(\xi):= \prod_{(x_i,u_i)\in \xi}g(x_i,u_i)$,
where $g(x,u)$ satisfies the property that
$g(x,u) = 1 $
for all $u \geq u_{*}$ for some $u_{*}>0$.

\subsubsection{Compact Containment Condition}
\begin{definition}
For any arbitrary $M,K>0$, 
we denote the set 
$$\mathcal{M}_{K,M}:= \{\mu \in \mathcal{M}(\mathbb{R^d} \times [0, \infty]): \mu([-M,M]^d \times [0,M])/M \leq K\}$$
to be the set of measures on $\IR^d \times[0,\infty)$ with mass smaller than $K$ in the region $[-M,M]^d \times [0,M]$.
\end{definition}

In Corollary \ref{cor: Vague Compact sets}, we will prove that $\mathcal{M}_{K,M}$ is vaguely compact.

\begin{lemma}[Compact Containment]
    \label{lem:lp_compact_containment}
Assume that $\xi^{N}_0 \to \xi_0$ weakly,
then for all $T>0$, there exists some constant $C(T)$,
such that
    \begin{align}
        \label{eqn:lp_mass_bound}
        \IE\left[
            \sup_{0 \le t \le T}
            \frac{1}{N}\langle 1, \xi^{N}_t \rangle
        \right]
        \le C(T) ,
    \end{align}
uniformly in $N$.
In particular, for any $\epsilon > 0$, there exists some $M_{\epsilon}>0, K_{\epsilon}>0$,
such that 
\begin{equation}
\limsup_{N \to \infty}
    \mathbb{P}\left\{ \xi^{N}_t \in \mathcal{M}_{K_{\epsilon},M_{\epsilon}}
        \text{ for } t\in [0,T] \right\}
        < \epsilon.
\end{equation}
\end{lemma}
\begin{proof}
By an application of Markov Mapping Theorem (see \S \ref{sec: Markov Mapping Theorem Application - Prelimit}), we know that

$$\left(\frac{1}{N}\langle 1, \xi^{N}_t(\cdot , [0, N]) \rangle\right)_{t \geq 0} \sim (\eta^N_t(\cdot ))_{t \geq 0},$$
i.e. the spatial projection of $(\xi^{N}_t)_{t \geq 0}$ has the same distribution as $(\eta^N_t)_{t \geq 0}$ defined in Definition \ref{defn:mgale_construction}. 
As a result, by Lemma \ref{lem:lp_compact_containment},
we have immediately that 
\begin{align}
        \IE\left[
            \sup_{0 \le t \le T}
            \frac{1}{N}\langle 1, \xi^{N}_t \rangle
        \right]
        = \IE\left[
            \sup_{0 \le t \le T}
            \langle 1, \eta^{N}_t \rangle
        \right]
        \le C(T) ,
    \end{align}
for some $C(T)>0$.

Moreover, we know that conditional on the spatial configuration 
$\frac{1}{N}\langle 1, \xi^{N}_t(\cdot , [0, N]) \rangle,$
the levels of each individual
is i.i.d uniformly distributed between $[0,N]$. 
Therefore, for $N>M_{\varepsilon}$
\begin{align*}
     \mathbb{P}\left\{ \xi^{N}_t \in \mathcal{M}_{K_{\epsilon},M_{\epsilon}}
        \text{ for } t\in [0,T] \right\}
        =& \mathbb{P}\left\{\sup_{ t\in [0,T]} \frac{1}{M_\varepsilon} \xi^{N}_t([-M_\varepsilon,M_\varepsilon]^d \times [0,M_\varepsilon]) \leq K_\varepsilon
         \right\}\\
         \leq& \frac{1}{M_\varepsilon K_{\varepsilon}} \mathbb{E}\left\{\sup_{ t\in [0,T]}  \xi^{N}_t([-M_\varepsilon,M_\varepsilon]^d \times [0,M_\varepsilon]) \right\}\\
        =& \frac{1}{M_\varepsilon K_{\varepsilon}}             \mathbb{E}_{\eta^N_t}\left\{ N \times
            \mathbb{E}\left[  
                \sup_{ t\in [0,T]}  \frac{1}{N}\xi^{N}_t([-M_\varepsilon,M_\varepsilon]^d \times [0,M_\varepsilon])
                \bigg| \eta^N_t
                        \right]
                    \right\}\\
        =& \frac{1}{M_\varepsilon K_{\varepsilon}} \mathbb{E}_{\eta^N_t}
                    \left\{ N \times
                    \sup_{ t\in [0,T]} \eta^{N}_t([-M_\varepsilon,M_\varepsilon]^d) \times \frac{M_{\varepsilon}}{N}
                    \right\}\\
        =& \frac{1}{K_{\varepsilon}} \mathbb{E}_{\eta^N_t}
                    \left\{
                    \sup_{ t\in [0,T]} \eta^{N}_t([-M_\varepsilon,M_\varepsilon]^d) 
                    \right\}\\
        \leq & \frac{1}{K_{\varepsilon}} \mathbb{E}_{\eta^N_t}
                    \left\{
                    \sup_{ t\in [0,T]} \langle 1, \eta^{N}_t \rangle 
                    \right\}\\
        < & \varepsilon.
\end{align*}
The first inequality holds by Markov's inequality, and the following two equalities hold as 
conditional on $\eta^N_t$,
$M_{\varepsilon}/N$ proportion of particles in $\xi^N_t$ have levels in $[0,M_{\varepsilon}]$. The final inequality holds as a direct consequence of \ref{lem:eta_compact_containment}.

We have therefore proved compact containment condition in the vague topology for our lookdown representation.
\end{proof}
\subsubsection{Tightness of $(F_g(\xi_t))_{t \geq 0}$}

@@

\begin{lemma}
For all $g \in \mathfrak{G}_{\leq 1}$, the processes $\{(F_g(\xi^N_t))_{t \geq 0}: N \in \mathbb{N}\}$ is tight as a real-valued stochastic process.
\end{lemma}
\begin{proof}

@@

\end{proof}
\section{Topological Results on Lookdown Representations}
\label{sec: Topologies on Lookdown}

\subsection{Euclidean-Vague Topology on $\IR^d \times [0,\infty]$}\label{sec: Convergence in Product Topology}
We first define a topology on $\IR^d \times [0,\infty]$ which is Euclidean on $\IR^d$ and vague in $[0,\infty]$.
\begin{definition}
We define the topology $\mathfrak{p}$ on $\IR^d \times [0,\infty]:$
we say $(x_n,u_n) \to (x,u)$ in topology $\mathfrak{p}$ if 
\begin{enumerate}
    \item $|x_n-x| \to 0$ in $\IR^d$.
    \item  For all $g \in C_{c}([0,\infty])$, the space of continuous functions with compact support on $[0,\infty]$, $g(u_n) \to g(u).$ Since this is the vague convergence for $(\delta_{u_n})_{n \in \mathbb{N}}$ we will abuse a bit the notation and denote this by the symbol $u_n \xrightarrow{vague} u$. 
\end{enumerate}
\end{definition}

In other words, our topology is Euclidean in space $\IR^d$ and vague in levels in $[0,\infty]$.
\begin{lemma}\label{Vague times Euclidean is Polish}
The space $\IR^d \times [0,\infty]$ under topology $\mathfrak{p}$ is Polish.
\end{lemma}
\begin{proof}
The space $C_c([0,\infty])$ is dense, so we pick a countable dense subset $S:=\{h_n: n \in \mathbb{N}\} \subset C^{1}_c([0,\infty])$ and define the metric $\mathfrak{d}$ such that $\mathfrak{d}(u,v)=\sum_{n=1}^{\infty}\frac{1 \wedge |h_n(u)-h_n(v)|}{2^n}$.

Assume that $u_n \xrightarrow{vague} u$. Pick arbitrary $\delta>0$ and take $N$ large enough such that $\frac{1}{2^N}<\delta/2$. Furthermore, pick $n$ large enough such that $\inf_{i=1,2,...,N}|h_i(u_n)-h_i(u)|<\delta/2$. From this we immediately have that $\mathfrak{d}(u_n,u)<\delta$. Thus $\mathfrak{d}(u_n,u) \to 0$.

Conversely assume that $\mathfrak{d}(u_n,u) \to 0$. For any $h \in \mathcal{C}^{1}_c([0,\infty])$ and for any $\delta>0$, pick $g_N$ such that $||h-h_N||_{\infty}<\delta /3$ and $n$ large enough such that $\mathfrak{d}(u_n,u)< \frac{\delta}{3 \times 2^N}$. Then $|h(u)-h(u_n)|< |h(u)-h_N(u)|+|h_N(u)-h_N(u_n)|+|h_N(u_n)-h(u_n)|<\delta$, and so $h(u_n) \to h(u)$.

Finally, one can easily check that $\mathbb{Q}$ is a countable dense set in $[0,\infty]$ equipped with the metric $\mathfrak{d}$.
Defining the metric $d_{\mathfrak{p}}$
by
$$d_{\mathfrak{p}}((x_1,u_1),(x_2,u_2))=||x_1-x_2||+\mathfrak{d}(u_1,u_2),$$
we can show easily that
convergence in $d_{\mathfrak{p}}$
is equivalent to convergence in 
$\mathfrak{p}$ topology.
\end{proof}

\subsection{Vague Topology on Measures}\label{sec: Empirical Measure Topology}

We now characterise the lookdown representation
of our particle system
as a measure on 
$(\IR^d \times [0, \infty], \mathfrak{p})$.
We endow the vague topology
on these measures for
convergence of lookdown representations.
We refer to Theorem A.23 and Theorem A.24 in \cite{kallenberg1997foundations}.

First of all,
as $(\IR^d \times [0, \infty], \mathfrak{p})$
is Polish,
the family of $C^{+}_K$ of continuous functions
$$f: \mathbb{R^d} \times [0, \infty] \to \IR^{+}$$
with compact support
is separable in the uniform metric. 
The sets $K_n =[-n, n]^d \times [0,n]$ clearly forms a sequence of compact sets and $K_n \uparrow \mathbb{R^d} \times [0, \infty]$.

We denote $\mathcal{M}(\mathbb{R^d} \times [0, \infty])$ as the class of measures on $\mathbb{R^d} \times [0, \infty]$ that are 
locally finite (i.e. bounded on bounded intervals),
and write $\pi_B, \pi_f$ 
for the mappings 
$\mu \to \mu B$, $\mu \to \mu f := \int f d\mu$,
respectively,
on $\mathcal{M}(\mathbb{R^d} \times [0, \infty])$.

The \textit{vague topology} in $\mathcal{M}(\mathbb{R^d} \times [0, \infty)$ is generated by the maps $\pi_f, f \in C^{+}_K$, and 
we write the cague convergence of $\mu_n$ toward $\mu$
as $\mu_n \xrightarrow{v} \mu$.

Taking $S= \mathbb{R^d} \times [0, \infty]$
in Theorem A.23
in \cite{kallenberg1997foundations},
we have
\begin{theorem}[vague topology]
\label{teo: Kallenberg vague results}

The following holds:
\begin{enumerate}
    \item $\mathcal{M}(\mathbb{R^d} \times [0, \infty])$ is a Polish space in the vague topology
    \item A set $A \subset \mathcal{M}(\mathbb{R^d} \times [0, \infty])$ is vaguely relatively compact iff 
    $\sup_{\mu \in A} \mu f < \infty$ for all $f \in C^{+}_K$
    \item if $\mu_n \xrightarrow{v} \mu$ and a set $B$ is finite with $\mu \partial B = 0$, then $\mu_n B \to \mu B$.
\end{enumerate}

\begin{corollary}
\label{cor: Vague Compact sets}
For any arbitrary $M,K>0$, the set 
$$\mathcal{M}_{K,M}:= \{\mu \in \mathcal{M}(\mathbb{R^d} \times [0, \infty]): M^{-1}\mu([-M,M]^d \times [0,M]) \leq K\}$$   
is a compact subset in 
$\mathcal{M}(\mathbb{R^d} \times [0, \infty])$ 
under the vague topology.
\end{corollary}
\begin{proof}
For any function $f \in C^{+}_K$, it is compactly supported and
so there exists a constant $C_f > ||f||_{\infty}$.
As a result, 
$$\sup_{\mu \in \mathcal{M}_{K,M}} \mu f < C_f \times \mu \{ supp(f) \cap [-M,M]^d \times [0,M]\} \leq C_f M^{-1} K < \infty.$$

Since $f$ is arbitrary, by (ii) of Theorem \ref{teo: Kallenberg vague results}, 
the set
$\mathcal{M}_{K,M}$
is vaguely relatively compact.

>>>>

    The process we consider is similar to the state-dependent branching processes
    of \citet{KR}, so one might expect that the proofs there would carry over with little change.
    However, there is an important difference:
    Recall that the level $U_a(t)$ of a line of descent evolves as
    $$
    \dot u 
    =
    c(x, \eta)
    u^2
    - b(x, \eta)
    u,
    $$
    where
    \begin{align*}
        c(x, \eta) &= \frac{\theta}{N} \gamma(x, \eta) \int_{\IR^d} r(y, \eta) q(x, dy) \\
        \text{and}\qquad
        b(x, \eta)
        &=
        \theta \gamma(x, \eta) \int_{\IR^d} \left(r(y, \eta) - r(x, \eta)\right) q(x, dy)
        + F(x, \eta) 
    \end{align*}
    (see equations \eqref{eqn:level_generator} and \eqref{eqn:b_limit}),
    where $c(x, \eta) \ge 0$ and $b(x, \eta)$ may take either sign.
    In \citet{kurtz/rodrigues:2011}, $b$ was bounded above and $c$ was bounded away from zero,
    so they noted that if $U_a(t) \ge b/c$
    lines of descent would only move upwards from that time onwards.
    This allows the processes to be jointly and simultaneously constructed
    for all values of $N$, with a pointwise embedding
    of $(\xi^N_t)_{t \ge 0}$ within $(\xi^{M})_{t \ge 0}$ for $b/c < N < M$.
    In other words, individuals with levels above $N > b/c$ at time $t_0$
    do not affect $(\lp^N_t)_{t \ge t_0}$,
    thus allowing a comparison of the number of lines of descent below level $u_0$
    to a branching process.
    Although we have provided a
    joint construction of $\lp^N$ for all $N$ in Section~\ref{sec: individual lines of descent},
    it does not have this monotonicity:
    for one thing, $b$ and $c$ depend on the population process $\eta$
    and so all individuals can affect all other ones (even those with lower levels).
    Furthermore, in the deterministic case $\theta/N$ and hence $c$ converge to zero,
    and so lines of descent with arbitrarily high level may drift back downwards.
    Indeed, this must be the case if the population persists,
    since in the deterministic case there is no branching.
    In our case $b$ and $c$ depend on the state of the population,
    so we have no such monotonicity.

@@

\begin{lemma} \label{lem:tightness of levels} For fixed $a\in \mathcal{U}$, let $U^N_{a}(\tau_a)=U_0$, i.e. the level of the line of descent $a$ at birth is $U_0>0$.
On top of the assumptions laid out in Lemma \ref{lem: tightness of individual spatial trajectory}, assume that 
$$
    \sup_{\theta}\mathbb{E}\left[ \sup_{x, \eta} b_\theta(x, \eta) \right]
    :=
    \sup_{\theta}
    \theta 
    \mathbb{E}\left[ \sup_{x, \eta} \left(
    \gamma_\theta(x,\eta) \int_{\IR^d} r_\theta(y, \eta) q_\theta(x, dy)
    -
    \mu_\theta(x,\eta)
    \right)\right] 
    \leq C_G,
$$
and there exists some $C_F \geq 0$ such that
\begin{align} 
\begin{split}
b_{\theta}(x, \eta)
&=
    \theta \gamma_{\theta}(x, \eta) \int_{\IR^d} \left( r_{\theta}(y, \eta) - r_{\theta}(x, \eta) \right) q_{\theta}(x, dy)
    + F_{\theta}(x, \eta) \\
& \geq - C_F \varrho_F*\eta(x)
\end{split}
\end{align}
for all $x \in \IR^d$ and  $\eta \in \mathcal{M}_{F}(\IR^d)$.

@@

\subsection{Tightness of the Lookdown Representation}
\begin{lemma}
The lookdown representation satisfies
Equation \eqref{eq: vague compact containment condition}, i.e.
for all $\epsilon>0$, there exists $N>0$ such that
\begin{equation}
 \limsup_{n \to \infty} \mathbb{P}\left\{ \sup_{t\in [0,T]}\langle f, \xi^n_t \rangle > N \right\} < \epsilon,
\end{equation}
\end{lemma}

\begin{proof}
For every $f \in C^{+}_{c}(\overline{\mathbb{R}^d} \times [0,\infty))$,
there exists $u^* > 0$ such that $f(x,u) = 0$ for all $u \geq u^*$.
Then,
\begin{equation}
\begin{aligned}
 &\limsup_{n \to \infty} \mathbb{P}\left\{ \sup_{t\in [0,T]}\langle f, \xi^n_t \rangle > N \right\} \\
 \leq & \limsup_{n \to \infty}\frac{\mathbb{E}\left\{ \sup_{t\in [0,T]}\langle f, \xi^n_t \rangle \right\}}{N}\\
 \leq & \limsup_{n \to \infty}||f||_{\infty}\frac{\mathbb{E}\left\{ \sup_{t\in [0,T]}\langle 1_{[0,u^*]}, \xi^n_t \rangle \right\}}{N}.
\end{aligned}
\end{equation}
Recall that conditional on 
$$ \frac{1}{n}\langle 1_{[0,n]}, \xi^n_t \rangle = \eta^n_t,$$
the level of each individual is independently and uniformly distributed between $[0,n]$.
Therefore, 
\begin{equation}
\mathbb{E}\left\{ \sup_{t\in [0,T]}\langle 1_{[0,u^*]}, \xi^n_t \rangle \right\} = u^* \mathbb{E}\left\{ \sup_{t\in [0,T]}\langle 1, \eta^n_t \rangle \right\}.
\end{equation}
Finally, 
recall that the supremum of the empirical measure process is controlled in Lemma \ref{lem:eta_compact_containment}
so there exists some constant $C_T$ such that 
\begin{equation}
\begin{aligned}
 &\limsup_{n \to \infty} \mathbb{P}\left\{ \sup_{t\in [0,T]}\langle f, \xi^n_t \rangle > N \right\} \\
 \leq & \limsup_{n \to \infty}||f||_{\infty}\frac{u^*}{N}\mathbb{E}\left\{ \sup_{t\in [0,T]}\langle 1, \eta^n_t \rangle \right\}\\
 \leq & ||f||_{\infty}\frac{u^*}{N}C_T\\
 < & \epsilon
\end{aligned}
\end{equation}
for sufficiently large $N$.
\end{proof}

It now suffices for us to show that the processes $\{(F_g(\xi^n_t))_{t \geq 0}: n \geq 1\}$ is relatively compact for all test functions $F_g$.
To do so, we apply Aldous criterion for real-valued processes.

\subsubsection{Tightness of $(F_g(\xi_t))_{t \geq 0}$}

@@

\begin{lemma}
For all $g \in \mathfrak{G}_{\leq 1}$, the processes $\{(F_g(\xi^N_t))_{t \geq 0}: N \in \mathbb{N}\}$ is tight as a real-valued stochastic process.
\end{lemma}
\begin{proof}
Once again, we intend to apply the Aldous Criterion. 
To do so, we need to prove that for all $\epsilon > 0$,
there exists $n_0 > 0$ and $\delta > 0$ such that 
\begin{equation}
\sup_{n \geq n_0}\sup_{\theta \in [0, \delta]}\mathbb{P}\{|F_g(\xi^n_{\tau+\theta})-F_g(\xi^n_{\tau})| > \epsilon\} < \epsilon
\end{equation} 
holds. 
It suffices to show that for sufficiently small $\delta > 0$,
$\limsup_{n \to \infty}\mathbb{E}[|F_g(\xi^n_{\tau_n + s})-F_g(\xi^n_{\tau_n})|^2] < \epsilon$
for all $\theta \in [0, \delta]$.

First, note that only events happening on particles with levels smaller than $u_g$ at time $\tau_n$ will contribute to the difference $|F_g(\xi^n_{\tau_n + s})-F_g(\xi^n_{\tau_n})|$.

To calculate this difference, we couple $(\xi^n_{\tau_n + s})_{s \in [0,\delta]}$ with the process $(\hat{\xi}^n_{\tau_n + s})_{s \in [0,\delta]}$ which has the same level dynamics as $(\xi^n_{\tau_n + s})_{s \in [0,\delta]}$ but with no birth. 
With this coupling, 
we have 
$\mathbb{E}[|F_g(\xi^n_{\tau_n + s})-F_g(\xi^n_{\tau_n})|^2] \leq 2\mathbb{E}[|F_g(\xi^n_{\tau_n + s})-F_g(\hat{\xi}^n_{\tau_n + s})|^2]+ 2\mathbb{E}[|F_g(\hat{\xi}^n_{\tau_n + s})-F_g(\xi^n_{\tau_n})|^2]$

We first try to control $\mathbb{E}[|F_g(\hat{\xi}^n_{\tau_n + s})-F_g(\xi^n_{\tau_n})|^2]$. 
This difference is simply influenced by the level dynamics. Therefore,
\begin{equation}
\begin{aligned}
 &\mathbb{E}[|F_g(\hat{\xi}^n_{\tau_n + s})-F_g(\xi^n_{\tau_n})|^2]\\
 \leq &
 \mathbb{E}\left[ \int_{0}^{\delta} \sum_{(x,u)\in\xi^n_{\tau_n+s}}\,
    \left|
        \frac{\theta}{n} \gamma(x,\eta) \int_{\IR^d} r(y, \eta) q_\theta(x, dy) u^2 -b_{\theta}(x,\eta)u
    \right|^2 \partial_u g(x,u)^2 ds\right]\\
 \leq & ||g'||_{\infty}
 \mathbb{E}\left[ \int_{0}^{\delta} \sum_{(x,u)\in\xi^n_{\tau_n+s}}\,
    \left| \frac{\theta}{n}  \gamma(x,\eta)  u_g^2 + (2  \gamma(x,\eta) + F(x,\eta))u_g
    \right|^2  ds\right] + O(1/\theta)\\
\leq & ||g'||_{\infty}u_g
 \mathbb{E}_{\eta}\left[ \int_{\tau_n}^{\tau_n+\delta} \int_{\mathbb{R}^d}
    \left| \frac{\theta}{n}  \gamma(x,\eta^n_{s})  u_g^2 + (2  \gamma(x,\eta^n_{s}) + F(x,\eta^n_{s}))u_g
    \right|^2 \eta^N_s(dx) ds\right] + O(1/\theta),
\end{aligned}
\end{equation}
so this term can be controlled with Lemma \ref{lem:tightness_for_F}.

We now control 
$\mathbb{E}[|F_g(\xi^n_{\tau_n + s})-F_g(\hat{\xi}^n_{\tau_n + s})|^2]$.
Note that this difference is purely contributed by the number of birth with both the parent and child having levels below $u_g$,
and the simple inequality 
$\mathbb{E}[|F_g(\xi^n_{\tau_n + s})-F_g(\hat{\xi}^n_{\tau_n + s})|^2] \leq 4 \mathbb{P}\{|F_g(\xi^n_{\tau_n + s})-F_g(\hat{\xi}^n_{\tau_n + s})|>0\}$
holds.

Therefore it suffices to prove that within a small interval of length $\delta > 0$,
the probability of such birth events happening is small.

This term can be controlled by the uniform boundedness of $\gamma(x,m)$.
For the birth event to contribute to the difference, the parent must have a level below $u_g$, and give birth to a child at level $u + \ell < u_g$.
Therefore, the total rate of relevant birth events satisfies
\begin{equation}
\sum_{(x,u) \in \xi^n_{\tau_n}([0,u_g] \times \overline{\mathbb{R}^d})}  \gamma(x,\eta^n_{\tau_n}) \mathbbm{1}_{u+ \ell < u_g }
\leq C_{\gamma} \xi^n_{\tau_n}([0,u_g] \times \overline{\mathbb{R}^d}.
\end{equation}
Therefore, with an application of Markov inequality, 
we have
\begin{equation}
\begin{aligned}
\mathbb{P}\{|F_g(\xi^n_{\tau_n + s})-F_g(\hat{\xi}^n_{\tau_n + s})|>0\}
\leq & \mathbb{P}[Poi(C_{\gamma} \xi^n_{\tau_n}([0,u_g] \times \overline{\mathbb{R}^d})s) \geq  1]\\
\leq & \mathbb{E}[Poi(C_{\gamma} \xi^n_{\tau_n}([0,u_g] \times \overline{\mathbb{R}^d})s)]\\
\leq & \mathbb{E}[Poi(C_{\gamma} \xi^n_{\tau_n}([0,u_g] \times \overline{\mathbb{R}^d})s)]\\
\leq & C_{\gamma}  \mathbb{E}[\xi^n_{\tau_n}([0,u_g] \times \overline{\mathbb{R}^d})]s\\
\leq & C_{\gamma}  u_g\mathbb{E}[\eta^n_{\tau_n}(\overline{\mathbb{R}^d})]s\\
<&  \epsilon.
\end{aligned}
\end{equation}

Combining all inequalities above, we have established Aldous Criterion and thus, tightness for the lookdown representation. 
\end{proof}

@@

\end{proof}
\section{Topological Results on Lookdown Representations}
\label{sec: Topologies on Lookdown}
\subsection{Topology for convergence of lookdown representations}

Recall that
the lookdown representation has a spatial component and a level component.
Specifically, for fixed $N>0$ and $t>0$,
the lookdown representation $\xi^N(t)$ 
is a finite measure on $\overline{\mathbb{R}^d} \times [0,N]$.

To characterise convergence of $\xi^N(t)$ as $N \to \infty$,
we therefore need to impose an appropriate topology on $\mathcal{M}(\overline{\mathbb{R}^d} \times [0,\infty))$,
the space of finite measures on $\overline{\mathbb{R}^d} \times [0,\infty)$.

We now refer to the vague topology introduced in P564, \S A2 in \cite{kallenberg1997foundations}.
Let $S$ be a locally compact Polish space and $\hat{S}$ be the class of bounded sets in $S$.
We consider the family $C^{+}_c(S)$ of positive continuous functions with compact support. It is known that $C^{+}_c$ is separable in the uniform metric.
We now consider $\mathcal{M}(S)$, the class of measures on $S$ that are locally finite.
The \textit{vague topology} on $\mathcal{M}(S)$ is generated by the the maps $\mu \to \mu f := \int f d \mu$, where $f\in C^{+}_{c}(S)$.
In other words, convergence of $\mu^n \to \mu$ in the vague topology holds if 
$$\int f d\mu^n \to \int f d\mu$$
for all $f\in C^{+}_{c}(S)$.

We now introduce two important theorems on compactness and convergence in the vague topology.
\begin{theorem}[Theorem A.23 in \cite{kallenberg1997foundations}]
For any locally compact, second-countable Hausdorff Space $S$, 
we have
\begin{itemize}
\item $\mathcal{S}$ is Polish in the vague topology,
\item a set $A\subset \mathcal{S}$ is vaguely relatively compact iff $\sup_{\mu\in A} \mu f < \infty$ for all $f \in C^{+}_{c}$
\item if $\mu_n \to \mu$ in the vague topology and $B \in \hat{S}$ with $\mu \partial B = 0$, then $\mu_n B \to \mu B$
\end{itemize}
\end{theorem}

The following corollary holds immediately.
\begin{corollary}
The set $\Gamma_K := \{\mu \in \mathcal{M}(S): \mu(S) \leq K\}$
is vaguely compact in $\mathcal{M}(S)$.
\end{corollary}
\begin{proof}
It suffices to show that $\Gamma_K$ is vaguely relatively compact and vaguely closed.
For any fixed $f \in C^{+}_c$,
we have that $ \sup_{\mu \in A} \mu f \leq  ||f||_{\infty} \mu(S)  \leq ||f|| K < \infty$,
so $\Gamma_K$ is vaguely relatively compact.

Now it suffices to prove that $\Gamma_K$ is closed under the vague topology.
Consider a vaguely converging sequence $(\mu_n)_{n \geq 1}$ in $\Gamma_K$
satisfying $\mu_n \to \mu \in \mathcal{M}(S)$,
then for an increasing sequence of functions $f_m \to 1$,
by the Dominating Convergence Theorem, 
\begin{equation}
\mu(S)
= \lim_{m \to \infty} \mu f_m
= \lim_{m \to \infty} \lim_{n \to \infty} \mu_n f_m
= \lim_{n \to \infty}   \mu_n (S)
\leq K,
\end{equation}
and so $\mu \in \Gamma_K$.
Therefore $\Gamma_K$ is vaguely compact. 
\end{proof}

We now include another theorem that is very relevant to establishing tightness of $\mathcal{M}(S)$-valued processes in the Skorokhod topology.

\begin{theorem}[Theorem A2.4 in \cite{kallenberg1997foundations}]\label{teo: vag_sko_conv}
Let $f_1,f_2,...$ be a dense collection in $C^{+}_{c}(S)$ closed under addition, 	
then any set $A \subset \mathcal{D}_{\mathcal{M}(S)}([0,\infty))$
is relatively compact if and only if for every $j \in \mathbb{N}$,
$Af_j = \{xf_j, x \in A\}$
is relatively compact in $\mathcal{D}_{\mathbb{R}^{+}}([0,\infty))$.
\end{theorem}

To characterise convergence of lookdown representations,
we take $S = \overline{\mathbb{R}^d} \times [0,\infty)$
and consider the test functions of the form 
\begin{equation}
F_g(\xi) = \prod_{(x,u) \in \xi} g(x,u),
\end{equation}
where $g(x,u)$ is differentiable in $u$, smooth in $x$.
and satisfies the property that $0\leq g(x,u) \leq 1$,
and that there exists $u^*$ such that for all $u > u^*$,
$g(x, u) =1$.

In fact, there is a one-to-one correspondence between $C^{+}_c(S)$
and test functions of the form $F_g$.
For all $f \in C^{+}_c(S)$,
if we write $g = e^{-f}$,
then
\begin{equation}
F_g(\xi)= e^{-\langle f, \xi \rangle}.
\end{equation}

Furthermore,
we know that for any $x_1, x_2 \in [0,N]$,
$$|x_1-x_2|\geq |e^{-x_1}-e^{-x_2}| \geq e^{-N}|x_1-x_2|,$$
so we can control $\langle f, \xi^n_t \rangle $ by controlling $F_g(\xi^n_t)$ as long as 
there exists some $N > 0$ such that $\langle f, \xi^n_t \rangle < N$.

Combining the above observation and Theorem \ref{teo: vag_sko_conv},
we have the following lemma.

\begin{lemma}
We consider a sequence $(\xi^n_t)_{t\geq 0}$ of $\mathcal{M}(\overline{\mathbb{R}^d} \times [0,\infty))$-valued cadlag processes.
Assume that for all test functions of the form $F_g$,
the sequence $\{(F_g(\xi^n_t))_{t \geq}: n=1,2,...\}$ of real-valued cadlag processes are relatively compact.

Furthermore, assume that for any $f \in C^{+}_{c}(\overline{\mathbb{R}^d} \times [0,\infty))$ and $\epsilon > 0$, there exists $N>0$ (dependent on $f$ and $\epsilon$), 
such that 
\begin{equation}
\label{eq: vague compact containment condition}
 \limsup_{n \to \infty} \mathbb{P}\left\{ \sup_{t\in [0,T]}\langle f, \xi^n_t \rangle > N \right\} < \epsilon,
\end{equation}

 then $(\xi^n_t)_{t\geq 0}$ is relatively compact in $\mathcal{D}_{\overline{\mathbb{R}^d} \times[0,\infty)}([0,T])$.
\end{lemma}
